Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
More results

% Chating in an IEA is a serious but common risk in volunteer based systems.  
% Future work could compare the use of gamification with out leaderboards
%

The results of each of the three experiments in terms of participation are detailed next.

@@

When comparing the networks of users, there is also a difference shown between experiments.

@@

Using the Neo4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. As an example, when comparing the
deployments B and GG based on their network of users (shown in figures \ref{fig:B-network} and \ref{fig:GG-network}
respectivly) additionaly to the differences in the number of nodes, certain patterns can also be observed.

>>>>

% Future work could compare the use of gamification with out leaderboards
%
The results of each of the three experiments in terms of participation are detailed next.

@@

@@

When monitoring the experiments, using the graph database and the Cypher query language 
provided interesting views on the connected data difficult to replicate with a relational database. 
As an example we can consider comparing the difference between the number of volunteers in deployments
B and GG,(shown in figures \ref{fig:B-network} and \ref{fig:GG-network} respectivly) additional
metrics and patterns are available when they are treated as a network. The same can be applied to 
the population, or the interaction as a whole. For instance when creating a new individual 
parents could be selected if there is a minimum distance between them in the graph.
